### 2014-06-22 paper.tex
renamed rnaseq_paper.tex to paper.tex

\subsection*{Expressed sequence tags and Genbank mRNA}
Expressed sequence tags (ESTs) and mRNAs were downloaded from UCSC genome website on May 9th, 2012.
The database last updated from GENBANK on April 29th, 2012.
Sequences were alignd to a chicken genome using BLAT.

>>>>

\subsection*{Expressed sequence tags and Genbank mRNA}
Expressed sequence tags (ESTs) and mRNAs were downloaded from UCSC genome website.
The database was updated from GENBANK on 1 January 2014.
Sequences were aligned to a chicken genome using BLAT.
